Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-15 vesicle_code/docs/adhesion/adhesion.tex
fixed some figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous drop
\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM,  DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity point) in an extensional flow is a saddle point
where two laminar streams converge along an axis and then diverge in a
different direction.  With an active control algorithm to fix the
position of the stagnation point by adjusting the streaming flow
strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
particle can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as PIV of
flow inside/around the particle.  To explore the application of such
fluid trap to measure the adhesion strength between two bound vesicle
membranes, we propose the following thought experiment.

@@

We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state doublet, the extensional
background flow is started.  We use this example to characterize the
required extensional rate to overcome the adhesive forces of the
doublet.  In particular, we investigate the effect of the reduced area.
For all the simulations, the length of the vesicles are fixed, while the
area is changed to achieve the desired reduced area.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous drop
\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM,  DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity point) in an extensional flow is a saddle point
where two laminar streams converge along an axis and then diverge in a
different direction.  With an active control algorithm to fix the
position of the stagnation point by adjusting the streaming flow
strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
particle can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as PIV of
flow inside and around the particle.  To explore the application of such
a fluid trap to measure the adhesion strength between two bound vesicle
membranes, we propose the following thought experiment.

@@

\todo[inline]{Start rewriting from here}
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state doublet, the extensional
background flow is started.  We use this example to characterize the
required extensional rate to overcome the adhesive forces of the
doublet.  In particular, we investigate the effect of the reduced area.
For all the simulations, the length of the vesicles are fixed, while the
area is changed to achieve the desired reduced area.
